The ChEMBL database as Linked Open Data

### 2012-03-02 article.tex
Restructuring: use cases around chosen technologies

This data set has been previously used in~\cite{Willighagen2011} ...

@@

@@

Ola: Use in BC-DS for possible adverse reactions.

Andra: CitedIn

The link between data and formal publication is important in many areas of
attribution, scientist ranking, etc, as outline in \cite{Waagmeester2012}.
ChEMBL contains many literature references, and we wish to query this data
for CitedIn.

@@

@@

@@

\# results of use cases

@@

Kasabi.

>>>>

This data set has been previously used in~\cite{Willighagen2011} and in Foo where the data is used
in the Foo framework (book chapter...)

@@

The RDF triples were generated from the a local MySQL chembl\_13 database populated with a stock
SQL dump of ChEMBL 13. PHP scripts were used to create N-Triples files. The source code is
available under a XXX license from https://github.com/egonw/chembl.rdf.

@@

A few new uses cases have been developed for this paper to demonstrate not just the intrinsic
value of the data in the ChEMBL database as done previously, but also to show the possibilities
the Linked Data nature offers.

... describe what we want to show ...

@@

\subsection{Data Statistics}

@@

The full set of triples are available from http://semantics.bigcat.unimaas.nl/chembl12/.

FIXME!

\subsection{Data Structure}

@@

\subsection{SPARQL end points}

\subsubsection{Bio2RDF}

Peter: write up the proxying... if that still works...

\subsubsection{Data Statistics and Validation}

%\subsubsection{CitedIn}

%Andra: use the SPARQL end point to find which entries in ChEMBL cite what papers

%The link between data and formal publication is important in many areas of
%attribution, scientist ranking, etc, as outline in \cite{Waagmeester2012}.
%ChEMBL contains many literature references, and we wish to query this data
%for CitedIn.

\subsubsection{Decision Support}

Egon,Antony/Valery,Ola: develop and write up the Bioclipse Decision Support use case

\subsection{Linked Data on Kasabi}

%\subsection{Use Case 2: Chem2Bio2RDF}

%David: Chem2Bio2RDF

\subsubsection{Linking out to ChemSpider}

Antony: if you can contribute ChemSpider IDs for the ChEMBL compounds ...

\subsubsection{Linking out to ChEMBL}

John/Anna: I can easily add links to webpages using foaf:homepage... are webpage URLs for entities stable enough?

\subsubsection{Linking out to Bio2RDF}

Peter/Egon: write up links to Bio2RDF for protein, pubmed, ...

@@

Tim and Foo of Kasabi. What S.H. Name of the Bioinformatics department at Uppsala University.
